Formalizing Stack Safety as a Security Property

### 2023-01-30 submission5/core.tex
Input instead of include
Comments on the new intro section
Detailed readthrough and notes on intro

\include{ideas-v1}

@@

\subsection{Public Allocations}

[TODO: this section could use some trimming. I think we have room for this
discussion, it's just more verbose than everything else and therefore feels weird.]

The full machine supports public stack allocations that can
be accessed by anyone until they are deallocated on their owner's return,
represented by \(\mathbf{alloc} ~ \mathbf{t} \dots\).
For example, consider the following code:

{\tt
  void g() \{

  ~ ~ int x[3];

  ~ ~ int y;

  ~ ~ h(\&x);

  \}
}

Here we have allocated several arrays and variables; {\tt y}
will behave as normal with \(\mathbf{alloc} ~ \mathbf{f} \dots\), but
{\tt x} has its address taken and passed to another function. That
function might do anything at all to {\tt x}, and might store its pointer
elsewhere (in the heap, for instance) so that the scope of legitimate accesses
to {\tt x} are uncertain. We default to assuming that any address-taken local
should be public. Meanwhile {\tt y} is still private.

In the likely event that the space for the return address, {\tt x}, and {\tt y}
are all allocated in a single step, that step makes multiple allocation operations:
\[\bar{\psi} = [\mathbf{alloc} ~ \mathbf{f} ~ (-20,4);
 \mathbf{alloc} ~ \mathbf{t} ~ (-16,12) ; \mathbf{alloc} ~ \mathbf{f} ~ (-4,4)]\]

Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
not sealed at a call. This makes these
regions of memory able to transmit information between caller and callee without
violating the stack safety properties. Note that there is no way to seal a location
once it has become \(\public\); only when {\tt x} is deallocated will its region
be available to allocate privately. We define a helper function, \(\mathit{range}\),
to map an offset from a register and a size into a set of addresses, and update
the operation's security semantics as shown in \cref{sfig:publicalloc}.

@@

    \caption{Argument Passing on }
    \label{sfig:stkargs}
  \end{subfigure}
  \caption{Operations}
  \label{fig:advops}
\end{figure*}

\subsection{Stack Arguments}

So far, we have not dealt with arguments spilled onto the stack, variadic arguments,
or arguments that are passed by reference without their addresses being taken
explicitly (i.e., structs and arrays passed directly.) Consider the simplest case,
where a function has more than 8 arguments and therefore must (in RISC-V) spill one
to the stack.

{\tt
  void main() \{

  ~ f(1,2,3,4,5,6,7,8,9);

  ~ g(42);

  \}
}

\begin{tabular}{r l | l}
  \labeledrow{0:}{addi sp,sp,-12}{\(\mathbf{alloc} ~ (-12,12)\)}
  \labeledrow{4:}{sd ra,4(sp)}{}
  \labeledrow{8:}{li a5,9}{}
  \labeledrow{12:}{sd a5,0(sp)}{}
  \labeledrow{16:}{li a7,8}{}
  \dots \\
  \labeledrow{48:}{jal 100,ra}{\(\mathbf{call} ~ \{\mathtt{a0-a7}\} ~ \{(\SP,0,4)\}\)}
  \labeledrow{52:}{li a0,42}{}
  \labeledrow{56:}{jal 200,ra}{\(\mathbf{call} ~ \{\mathtt{a0}\} ~ \emplist\)}
  \dots \\
\end{tabular}

Under a typical calling convention, the callee expects the ninth argument to
be passed to it at bottom of the caller's frame, so the caller allocates extra
space for it. Then the call to {\tt f} identifies that we expect a range of four
bytes from the stack pointer to be passed as an object instead of sealed.

So we must refine our call operation to make use of the information that we have about
which memory contain arguments, \(\overline{sa}\). \(\overline{sa}\) is a set of
triples of a register, an offset from the value of that register, and a size.
We first define the helpful set \(\mathit{passed} ~ \overline{sa} ~ \mach\),
then extend the call operation to keep all objects in \(\mathit{passed}\) marked
as \(\object\) and seal everything else (\cref{sfig:stkargs}).

The remaining definitions are unchanged. Now a stack-spilled argument can be allocated
and remain accessible in the callee, while its memory is sealed for calls that do not
use that memory as an argument.

This same structure works for pass-by-reference arguments. In this case {\tt main}
passes an array {\tt x} directly, which is compiled as a pass-by-reference.

{\tt
  int main() \{

  ~ int x[1];

  ~ f(x);

  ~ g();

  ~ return x[0];

  \}
}

Unlike the address-taken array, we can clearly delineate the scope in which {\tt x} may be
accessed without violating stack safety: {\tt f} should be allowed to access it, but further
calls from {\tt f} should not (unless {\tt f} passes it to them) and {\tt g} certainly
should not. Say the compiler opts to pass the pointer to {\tt x} in register {\tt a0}.
The {\tt f} is specifically being given access to the four bytes starting at that address.
The call operation is \(\mathbf{call} ~ \emplist ~ \{(\mathtt{a0},0,4)\}\).

@@

\section{Related Work}
\label{sec:relwork}

\paragraphx{Formal Stack Safety on Capability Machines}
%
To our knowledge, the only line of work to date that has attempted
a positive and formal characterization of stack safety
begins with Skorstengaard et al. \cite{SkorstengaardSTKJFP} and is improved
by Georges et al. \cite{Georges22:TempsDesCerises}. The former's
StkTokens system enforces stack safety on hardware equipped with
memory capabilities, similar to those used in the Cheri system~\cite{Woodruff+14,Chisnall+15}, but
with additional support for linear capabilities, while the latter offer a calling
convention that can replace the expensive and likely-impractical linear capabilities
with more efficient ``directed'' capabilities.

Both works define stack safety as the conjunction of local state encapsulation (LSE) and
well-bracketed control flow (WBCF).
Informally, LSE means that the current activation can only access its own frame,
and WBCF means that the topmost frame can only return to
the immediately adjacent frame below. Formally, these properties are defined
with reference to a capability machine with a built-in call stack and call and return
instructions; this machine is proven fully abstract with respect to a more
concrete capability machine, an approach termed ``fully abstract overlay semantics.''

[TODO: more detailed comparison with Aina's work primarily.]

\paragraphx{Heap Safety as a Security Property}
%
Azevedo de Amorim et al.~\cite{DBLP:conf/post/AmorimHP18} show that
heap safety may be framed as a security property using
the language of noninterference. Their paper was a significant inspiration
for the present work, and we believe that their safety conditions should
combine smoothly into ours.

>>>>

\input{ideas-v2}

@@

\subsection{Sharing Stack Memory}

In our examples so far, we have presented a vision of stack safety in which
the interface between caller and callee is in the registers that pass
arguments and return values. This is frequently not the case in a realistic
setting. Arguments may be passed on the stack due to being spilled, as an implementation
of variadic arguments, or because they are reference objects that inherently have
pass-by-reference semantics. The caller may also take the address of a local object and
pass that as a pointer to its callee.

We refine our call operation to make use of the information that we have about
which memory contain arguments, \(\overline{sa}\). \(\overline{sa}\) is a set of
triples of a register, an offset from the value of that register, and a size.
We first define the helpful set \(\mathit{passed} ~ \overline{sa} ~ \mach\),
then extend the call operation to keep all objects in \(\mathit{passed}\) marked
as \(\object\) and seal everything else (\cref{sfig:stkargs}).

In this mechanism, we can describe an argument being passed by their relative address
with the operation \(\mathbf{call} ~ \dots ~ (\SP, \mathit{off}, \mathit{sz})\).
In the case of pass-by-reference semantics, if the compiler designates register
\(\reg\) as holding the reference, then the operations is
\(\mathbf{call} ~ \dots ~ (\reg, 0, \mathit{sz})\).

In both cases, the immediate callee retains access to the passed object, but future
callees will not---unless the object is passed-by-reference further down the stack.
On the other hand, in the case of a caller explicitly taking the address of an
object and passing it as a pointer, we have no way obvious way to limit the scope
of such sharing.

Our primary machine treats this scenario as the caller allocating a ``public''
object that can be accessed by anyone until it's deallocated. We extend the
\(\mathbf{alloc}\) operation with a boolean flag, where {\bf t} indicates
that the allocation is public, and {\bf f} is private.
In the likely event that the space for multiple objects is allocated in a single step,
that step can make multiple allocation operations, each labeled appropriately.
Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
never sealed at a call (\cref{sfig:publicalloc}).

@@

    \caption{Calls with Argument Passing on the Stack}
    \label{sfig:stkargs}
  \end{subfigure}
  \caption{Operations}
  \label{fig:advops}
\end{figure*}

@@

### 2023-01-30 submission5/intro-v2.tex
Detailed readthrough and notes on intro

Computer programming at any scale relies on \emph{functions} (variously known as
subroutines, procedures, methods, etc.) as a \emph{foundational abstraction} to
structure programs into building blocks representing units of computation that
can \emph{call} one another to create larger computations.
%
At a low level, a function call comprises its own data (private or shared), as
well as information about its \emph{caller} and \emph{callee} functions. The
runtime must keep track of the local contexts of all function activations
at any given time; the \emph{fundamental data structure} charged with realizing
this abstraction is the \emph{(call) stack}.
%
\rb{This should be well known, so no need for illustration?}

\sna{I agree, but: a discussion of the low-level abstraction should discuss
  the ABI and the fact that things like private vs. shared data are fundamentally
  not specified.}

The correct execution on a program---and its security!---is contingent on all of
its functions properly implementing this abstraction by means of a careful use
of the call stack. Be it accidental or intentional, incorrect management of the
stack is at the root of a myriad of faults whose effects range from (rarely)
innocuous to (usually) catastrophic.
%
From a security perspective, attacks on the stack (say, from a malicious
function that chooses to abuse its access to the contents of this data
structure) are as fundamental, varied and pervasive as the functional
abstraction itself.
%
\rb{Begins to prefigure the idea of multiple stack implementations.}

@@

Indeed, the call stack is a perennial target for low-level attacks, leading to
dire consequences, from leakage and corruption of private stack data
to control-flow hijacking.
%
Even a cursory glance at the most recent release of the authoritative CWE Top 25
Most Dangerous Software Weaknesses
list\footnote{\url{https://cwe.mitre.org/top25/archive/2022/2022_cwe_top25.html}}
shows general classes of vulnerabilities closely related to the stack \rb{(though not exclusively)}
consistently at and near the top, e.g., \#1 (CWE-787, Out-of-bounds Write), \#5 (CWE-125, Out-of-bounds Read), \#7 (CWE-416, Use
After Free) or \#11 (CWE-476, NULL Pointer Dereference).
%
Moreover, many other types of faults involve some kind of control or data flow
using data stored in the stack \rb{cf. Eternal war in memory, Google/Microsoft
memory safety statistics, etc.}.
%
To foil such attacks, a menagerie of
software and hardware protections have been proposed,
%
including stack canaries~\cite{Cowan+98},
bounds checking~\cite{NagarakatteZMZ09,NagarakatteZMZ10,DeviettiBMZ08},
split stacks~\cite{Kuznetsov+14},
shadow stacks~\cite{Dang+15,Shanbhogue+19},
capabilities~\cite{Woodruff+14,Chisnall+15,SkorstengaardLocal,SkorstengaardSTKJFP,Georges+21},
and hardware tagging~\cite{DBLP:conf/sp/RoesslerD18}---we discuss these in more
detail in \cref{XXX}.
  \ifaftersubmission\apt{Mostly from
  nick; there could be more}\bcp{Yes, going back to MIT days---we should
  include several more of these, if only to give readers the impression that
this is a well-studied mechanism (so formalizing its protections is
useful).}
\fi
%
\rb{Broad enough? Do we want to add more techniques?}
%
Yet despite this wealth of potential solutions, the stack remains a central
security concern---why?

Security mechanisms designed to prevent a certain attack can be brittle---successfully
eliminating the attack as it exists at the time of publication, but leaving room for attackers
to find new, similar attacks.
%
%% \rb{And so the cat-and-mouse game continues.}
%
To mitigate this risk, \rb{we claim that} mechanisms should aim to enforce \emph{formal
properties} of safe behavior that can be proven or tested. Such properties become the
\emph{specification} against which enforcement can be validated; even enforcement mechanisms that do
not fulfill a property benefit from the ability to articulate \emph{why} they fail.
%
%% \rb{Good stuff! There is some overlap between this discussion and the opening
%%   motivation, maybe we could restructure things a bit so that those threads are
%%   unified?}
%
This is the problem we begin to address in this paper \rb{or a few more such
  connecting words}.

\subsection{A Menagerie of Stack Protection Mechanisms}

\rb{A.K.A. related work (part 1?). I wonder if this goes before or after a first
  look at the idea of the properties.}

@@

In addition to the many software-based techniques developed to provide greater
degrees of protection to the stack, often incurring a significant performance penalty,
some proposals have turned to specialized hardware features to offset those
costs and attempt to offer greater levels of protection.
%
\rb{Something about how realistic/practical these alternatives are? Are we
  selecting partly based on prototypes, etc.?}

@@

\sna{If we have good examples of other capability systems, we should absolutely
  talk about them. No need to privilege CHERI.}
%
Capability machines can represent and manipulate
unforgeable tokens of authority over specific regions of
memory using a combination of dedicated out-of-band memory and
specialized ISA instructions.
%
The most prominent contemporary representative of this long line of work is
CHERI \cite{}, a modern architecture designed to provide efficient fine-grained
memory protection and compartmentalization.
%
Previous work has uses these principles in simplified models to implement
\emph{secure calling conventions} for the call
stack \cite{}. Those conventions can be seen as combining the
protections of bounds-checking with software-based methods of control-flow protection.
%
They are closely related \rb{too strong?} to this work; we discuss them in more
detail in \cref{XXX}.
%
\rb{HardBound is also related to this}

@@

As we begin to intuit, the security of the call stack and its contents can be
viewed through many different lenses. Each of these points of view results in a
\emph{unique specification} of the meaning of \emph{stack safety} for a
particular protection mechanism---usually an informal specification if one is
produced, and almost always left implicit to some degree.
%
Moreover, different protections operate under different threat models, further
complicating their comparison and the assessment of the safeguards they
effectively offer their clients---the programs themselves.
%
On the face of it, it seems perplexing that there is not a \emph{standard
specification} (or set of specifications) for such a fundamental problem.
Instead of reverse-engineering a specific enforcement mechanism to obtain a
(necessarily approximate) specification, we turn the problem around on its head
and seek more general solutions from first principles.
%
\rb{(Problems/notes: ``backward specs'' not the most useful to their clients,
  not designed with their security needs in mind---goes in the direction of
  program logics---; to reason about security in complex systems an explicit and
  clear spec is preferable; many of the informal specs are at least
  superficially similar and overlapping; hopefully all of them can be understood
  from a small number of fundamental concepts)}

\sna{Still very worried about whether this is plausible to claim given our focus
  on one enforcement mechanism. There is probably a way to thread the needle, though.
  Something like: we begin with a mechanism that we know is not supported by any
  other model, and seek to build a model that is not specific to it by appealing to
  first principles.}

We propose a novel characterization of stack safety using the formal tools of language-based
security~\cite{sabelfeld2003language}, decomposing stack safety into
the {\em integrity} and {\em confidentiality} of the caller’s local state
and the callee's behavior during the callee's execution, plus the control-flow protection
of {\em well-bracketed control flow}~\cite{SkorstengaardSTKJFP} (\(\wbcf\)).
\ifexceptions
We also extend WBCF to a setting with exceptions,
in which there may be multiple points at which a callee can ``return.''
\fi
%
We treat stack safety as multiple properties, rather than one multi-faceted property, because
not all enforcement mechanisms attempt to implement all aspects of stack safety. Some focus
exclusively on control flow, some enforce integrity but not confidentiality, and many
focus on the caller over the callee.
%
\rb{Return to this after extended discussion? Forward ref?}
%
This gives us a total of five core properties: \(\wbcf\),
caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
callee integrity (\(\clei\)), and callee confidentiality (\(\clec\)).
%
\rb{Forward references?}

We are not attempting to create a universal definition of stack safety for all systems.
Rather, we define the stack safety of a single, fairly realistic system, decomposed into
(1) a lightweight model of the system and its security-relevant features, from which we
derive the integrity, confidentiality, and control-flow requirements of each call and
return, (2) the application of that model to a particular target system, and (3)
the formal criteria for integrity, confidentiality, and control flow
to obey the requirements. We consider the criteria in (3) to represent universal definitions
that are parameterized by (1).
%
\rb{FIXME: Contrast some universal definitions (or a parametric framework) with
  the concrete instance we study, again with its interest properly motivated.
  (Coming in key ideas?) No ``gold standard''?}

Stack safety is challenging to specify in full generality, because the stack is fundamentally
an architecture-specific construct. (Contrast Azevedo de Amorim et al.'s \cite{DBLP:conf/post/AmorimHP18} work on heap safety,
which is broadly consistent across architectures and language semantics, and therefore amenable
to a very general approach.)
The desired behavior of the stack varies based on ISA, calling convention,
and the features of whichever programming language originated the code.
%
\rb{(Extremely important!)}
%
For instance, the current state-of-the-art stack-safety specification from Georges et al.
\cite{Georges22:TempsDesCerises} supposes a machine with only straightforward call-and-return
control flow, and therefore defines {\it Well-bracketed Control Flow} (WBCF) under the assumption that
a callee should always return to its caller. But, in the presence of tail-call elimination, a
return from a callee to a distant ancestor is perfectly reasonable. Any addition of new features
must be accompanied by tweaks to the model.
%
\rb{(Make this second point later?)}

>>>>

Computer programming at any scale relies on \emph{functions} (variously known as
subroutines, procedures, methods, etc.) as a \emph{foundational abstraction} to
structure programs into building blocks representing units of computation that
can \emph{call} one another to create larger computations.
%
At a low level, a function call comprises its own data (private or shared), as
well as information about its \emph{caller} and \emph{callee} functions. The
runtime must keep track of the local contexts of all function activations
at any given time; the \emph{fundamental data structure} charged with realizing
this abstraction is the \emph{(call) stack}. But at the level of the ABI
\sna{Do we need to unpack the acronym ABI?}, the specification of a well-behaved
stack is minimal. It is not concerned with such questions as whether a caller's
frame should be readable or writable to its callee, leaving those concerns
to be determined by a high-level language built atop the stack.

The correct execution---and the security!---of a program is contingent on all of
its functions properly implementing the intended abstraction by means of a careful use
of the call stack. Be it accidental or intentional, incorrect management of the
stack is at the root of many faults whose effects range from (rarely)
innocuous to (usually) catastrophic.
%
From a security perspective, attacks on the stack (say, from a malicious
function that chooses to abuse its access to the contents of this data
structure) are as fundamental, varied and pervasive as the functional
abstraction itself.
%

@@

Indeed, the call stack is a perennial target for low-level attacks, leading to
dire consequences, from leakage and corruption of private stack data
to control-flow hijacking.
%
The most recent release of the authoritative CWE Top 25
Most Dangerous Software Weaknesses
list\footnote{\url{https://cwe.mitre.org/top25/archive/2022/2022_cwe_top25.html}}
shows general classes of vulnerabilities closely related to the stack \rb{(though not exclusively)}
consistently at and near the top, e.g., \#1 (CWE-787, Out-of-bounds Write), \#5 (CWE-125, Out-of-bounds Read), \#7 (CWE-416, Use After Free) or \#11 (CWE-476, NULL Pointer Dereference).
%
Moreover, many other types of faults involve some kind of control or data flow
using data stored in the stack \rb{cf. Eternal war in memory, Google/Microsoft
  memory safety statistics, etc.}.
\sna{Trying to think how to make the case that these CWEs are about the stack, since they are
  primarily described as memory attacks.}
%
To foil such attacks, a menagerie of
software and hardware protections have been proposed,
%
including stack canaries~\cite{Cowan+98},
bounds checking~\cite{NagarakatteZMZ09,NagarakatteZMZ10,DeviettiBMZ08},
split stacks~\cite{Kuznetsov+14},
shadow stacks~\cite{Dang+15,Shanbhogue+19},
capabilities~\cite{Woodruff+14,Chisnall+15,SkorstengaardLocal,SkorstengaardSTKJFP,Georges+21},
and hardware tagging~\cite{DBLP:conf/sp/RoesslerD18}---we discuss these in more
detail in \cref{XXX}.
  \ifaftersubmission\apt{Mostly from
  nick; there could be more}\bcp{Yes, going back to MIT days---we should
  include several more of these, if only to give readers the impression that
this is a well-studied mechanism (so formalizing its protections is
useful).}
\fi
%
\rb{Broad enough? Do we want to add more techniques?}
\sna{I think this is plenty unless there's a really major thing we're forgetting.}
%
Yet despite this wealth of potential solutions, the stack remains a central
security concern.

\paragraph{Formal Properties}

Security mechanisms designed to prevent a certain attack can be brittle---successfully
eliminating the attack as it exists at the time of publication, but leaving room for attackers
to find new, similar attacks.
%
%% \rb{And so the cat-and-mouse game continues.}
%
To mitigate this risk, we claim that mechanisms should aim to enforce \emph{formal
properties} of safe behavior that can be proven or tested. Such properties become the
\emph{specification} against which enforcement can be validated; even enforcement mechanisms that do
not fulfill a property benefit from the ability to articulate \emph{why} they fail.
%
%% \rb{Good stuff! There is some overlap between this discussion and the opening
%%   motivation, maybe we could restructure things a bit so that those threads are
%%   unified?}
%
Our work is focused on the creation of such properties for stack safety.

\subsection{Related Work}

@@

In addition to the many software-based techniques developed to provide greater
degrees of protection to the stack, often incurring a significant performance penalty,
some proposals have turned to specialized hardware features to offset those
costs and attempt to offer greater levels of protection.

We focus in particular on two families of hardware mechanisms: capability machines
and tag-based reference monitors. Both types of system move beyond simply
offering hardware acceleration for software-based techniques, offering hardware
primitives for both memory and control-flow enforcement that can offer a degree
of protection even with minimal cooperation from the code.
%
\rb{Something about how realistic/practical these alternatives are? Are we
  selecting partly based on prototypes, etc.?}

@@

\sna{If we have good examples of other capability systems, we should absolutely
  talk about them. No need to privilege CHERI.}
%
Capability machines can represent and manipulate
unforgeable tokens of authority over specific regions of
memory using a combination of dedicated out-of-band memory and
specialized ISA instructions.
%
The most prominent contemporary representative of this long line of work is
CHERI \cite{}, a modern architecture designed to provide efficient fine-grained
memory protection and compartmentalization.
%
Previous work has uses these principles in simplified models to implement
\emph{secure calling conventions} for the call
stack \cite{}. Those conventions can be seen as combining the
protections of bounds-checking with software-based methods of control-flow protection.
%
They are closely related \rb{too strong?} to this work; we discuss them in more
detail in \cref{XXX}.
%

@@

We begin to see that the security of the call stack and its contents is not
clearly defined. Different protection mechanisms aim to protect the stack
in fundamentally different ways, each offering a \emph{unique}, \emph{implicit}
specification of the meaning of ``stack safety.'' These specifications
may be more or less compatible with the needs of a given high-level language.
Moreover, different protections operate under different threat models, further
complicating their comparison and the assessment of the safeguards they
effectively offer their clients---the programs themselves.
It would be far preferable to have a \emph{standard}, \emph{explicit} specification.
Only a handful of works have offered any explicit specification.

Stack safety is challenging to specify in full generality, because the stack is
fundamentally an architecture-specific construct.
(Contrast Azevedo de Amorim et al.'s \cite{DBLP:conf/post/AmorimHP18} work on heap safety,
which is broadly consistent across architectures and language semantics, and therefore
amenable to a very general approach.)
The desired behavior of the stack varies based on ISA, calling convention,
and the features of whichever programming language originated the code.
%
For instance, the current state-of-the-art stack-safety specification from Georges et al.
\cite{Georges22:TempsDesCerises} supposes a machine with only straightforward call-and-return
control flow, and therefore defines {\it Well-bracketed Control Flow} (WBCF) under the assumption that
a callee should always return to its caller. But, in the presence of tail-call elimination, a
return from a callee to a distant ancestor is perfectly reasonable.

In this work, we propose an explicit specification, built from first principles
in the hopes that it will be widely applicable, and demonstrate that it supports
an enforcement mechanism that does not yet have one.
We use the formal tools of language-based
security~\cite{sabelfeld2003language}, decomposing stack safety into
the {\em integrity} and {\em confidentiality} of the caller’s local state
and the callee's behavior during the callee's execution, plus the control-flow protection
of {\em well-bracketed control flow}~\cite{SkorstengaardSTKJFP} (\(\wbcf\)).
\ifexceptions
We also extend WBCF to a setting with exceptions,
in which there may be multiple points at which a callee can ``return.''
\fi
%
We treat stack safety as multiple properties, rather than one multi-faceted property, because
not all enforcement mechanisms attempt to implement all aspects of stack safety. Some focus
exclusively on control flow, some enforce integrity but not confidentiality, and many
focus on the caller over the callee.
%
\rb{Return to this after extended discussion? Forward ref?}
%
This gives us a total of five core properties: \(\wbcf\),
caller integrity (\(\clri\)), caller confidentiality (\(\clrc\)),
callee integrity (\(\clei\)), and callee confidentiality (\(\clec\)), defined formally
in \cref{sec:props}.
%

We are not attempting to create a universal definition of stack safety for all systems.
Rather, we define the stack safety of a single, fairly realistic system, decomposed into
(1) a lightweight model of the system and its security-relevant features, from which we
derive the integrity, confidentiality, and control-flow requirements of each call and
return, (2) the application of that model to a particular target system, and (3)
the formal criteria for integrity, confidentiality, and control flow
to obey the requirements. This decomposition can be thought of as a step toward
a universal definition, in that the definitions in (3) capture fundamental
notions of security that can then be applied flexibly to other systems by varying
the model in (1) and (2).
%
\rb{FIXME: Contrast some universal definitions (or a parametric framework) with
  the concrete instance we study, again with its interest properly motivated.
  (Coming in key ideas?) No ``gold standard''?}

\sna{Not sure what your FIXME means exactly. Can you elaborate?}
